---
title: README
author: Xiaoyi Wang
date: 03/07/2024
date-format: long
format: 
  html: 
    self-contained: true
    df-print: tibble
editor_options: 
  chunk_output_type: console
execute: 
  warning: false
  message: false
---

Install packages.

```{r, setup}
pacman::p_load(tidyverse, targets, gt, readxl, quarto)
```

Because we want to obtain Christmas movies, therefore:

1.  Retain movie information that includes title types "movie" and "tvMovie", treating them as belonging to the movie category.

2.  Retain movie information where "christmas" is true.

Then, only retain the genres and average ratings of the filtered movie information.

For readability, display only the first 10 rows of the table, and show only one decimal place.

```{r}
tar_read(movies_tab1_show)
```

Categorize movies by genre, calculate the average and median ratings for each genre, and then rank the genres and their median ratings in descending order according to the mean ratings.

It is worth noting that the initial classification of genres from the original Excel file will be maintained. For example, "Comedy" and "Comedy, Drama" will be considered as two different genres.

For readability, display only the first 10 rows of the table, and show only one decimal place.

```{r}
tar_read(movies_tab2_show)
```

If available, obtain genres with both mean and median ratings higher than those of others.

```{r}
tar_read(movies_answer)
```

Ultimately, we conclude that the genre "Documentary, History, War" provides the best rating for Christmas movies.
